Digital History in Finland, 1488-1828

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

```{r topics44, echo=TRUE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
selections = list(
  c("kirkkohistoria","raamatunhistoria","eksegetiikka","homiletiikka","dogmatiikka","teologia"),
  c("oppihistoria","antiikki","historia"),
  c("filosofia","luonnonfilosofia","metafysiikka","logiikka"),
  c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia"),
  c("retoriikka","poetiikka","kielitiede","kielioppi"),
  c("heprean kieli","kreikan kieli","latinan kieli"),
  c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus"),
  c("luonnonhistoria","lääketiede","tartuntataudit","eläintiede","kasvitiede","kasvisto","eläimet","eläinsuojelu","eläimistö","eläintaudit","hevonen"),
  c("naiset","naisen asema","naisasialiikkeet","naisasiajärjestöt"),
  c("etsintäkuulutukset","rikokset","oikeus","rangaistukset"))

>>>>

```{r topics44, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
selections = list(
  c("kirkkohistoria","raamatunhistoria","eksegetiikka","homiletiikka","dogmatiikka","teologia"),
  c("oppihistoria","antiikki","historia"),
  c("filosofia","luonnonfilosofia","metafysiikka","logiikka"),
  c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia"),
  c("retoriikka","poetiikka","kielitiede","kielioppi"),
  c("heprean kieli","kreikan kieli","latinan kieli"),
  c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus"),
  c("luonnonhistoria","lääketiede","tartuntataudit","eläintiede","kasvitiede","kasvisto","eläimet","eläinsuojelu","eläimistö","eläintaudit","hevonen"),
  c("naiset","naisen asema","naisasialiikkeet","naisasiajärjestöt"),
  c("etsintäkuulutukset","rikokset","oikeus","rangaistukset"))
